\documentclass[10pt]{article}

\usepackage[a4paper, total={7in, 10.5in}, includehead]{geometry}
\usepackage{parth-article}
\usepackage{sensible-macros}
\usepackage[fixed]{fontawesome5}
\addbibresource{~/Notebook/.meta/zotero-library.bib}

\setmainfont{baskervaldx}[Numbers={Proportional, OldStyle}]

\newcommand{\nextItem}{\\[0.25em]}
\newcommand{\nextSection}{\\[0.5em]}
\newcommand{\subtext}[1]{%
    \\[0.25em]&&%
    \begin{minipage}[c]{4.3in}%
        #1%
    \end{minipage}%
    \\\\[-0.6em]%
}


\rfoot{\normalsize Last updated \today}
%\cfoot{\normalsize \href{mailto:pas201@srcf.net}{\texttt{pas201@srcf.net}} \qquad\qquad \url{pas201.user.srcf.net}\\}

\begin{document}
\title{
	\vspace{-1em}
	Parth Shimpi\normalsize%\orcidlink{0009-0008-2066-7474}
	\raisebox{-0.1em}{\huge\(\phantom\vert\)}
	\raisebox{0.3em}{
		\begin{minipage}[c]{0in}
			\href{mailto:pas201@srcf.net}{\tiny{\faEnvelope[regular]}~\small{pas201@srcf.net}}\\[-0.4em]
			\href{https://pas201.user.srcf.net}{\tiny{\faLink}~\small{pas201.user.srcf.net}}
		\end{minipage}}}
%
%    \normalsize\ \raisebox{0.1em}{Curriculum
%vitae}\\[0.3em]\small() \quad
%()}
\date{}
\pagenumbering{gobble}
\maketitle
\thispagestyle{fancy}
\vspace{-5.5em}
\begin{longtable}{>{\raggedleft\arraybackslash}p{0.8in}>{}p{0.05in}>{}p{5.7in}}
	Education%
	 &  & \textbf{PhD in Mathematics},
	University of Glasgow
	\hfill Expected 2026                                                                   \\
	 &  & Advisor Prof.\ Michael Wemyss.\nextItem%
	 &  & \textbf{MMath (Part III)},
	University of Cambridge
	\hfill 2022                                                                            \\
	 &  & Merit. Essay title `\emph{Derived equivalences in Algebra and
		Geometry}'.
	\nextItem%
	 &  & \textbf{BA in Mathematics},
	University of Cambridge
	\hfill 2021                                                                            \\
	 &  & First class honours.
	\nextSection%
	Awards%
	 &  & \textbf{ERC Scholarship}, European Research Council\hfill 2022                   \\
	 &  & Award towards doctoral education.\nextItem%
	 &  & \textbf{Stephen Hawking Award}, Gonville and Caius College,
	Cambridge. \hfill 2021\nextItem%
	%        && \textbf{Elected into scholarship}, Gonville and Caius College, Cambridge. \hfill 2019, 2020, 2021\nextItem
	 &  & \textbf{Examination Prize}, Gonville and Caius College, Cambridge.
	\hfill 2019, 2021\nextItem%
	 &  & \textbf{Cambridge Trust Scholarship}, Cambridge Trust \hfill 2018                \\
	 &  & Award of £40,000 towards undergraduate education.\nextItem%
	 &  & \textbf{Overseas scholarship}, Gonville and Caius College, Cambridge \hfill 2018 \\
	 &  & Award of £40,000 towards undergraduate education.\nextSection%
	\multirow{2}{0.8in}{\raggedleft\arraybackslash Publications \& preprints}%
	 &  & Simple complexes on a flopped curve \hfill 2025                                  \\
	 &  & \emph{Preprint.}
	\href{https://arxiv.org/abs/2508.06437}{arXiv:2508.06437}
	\nextItem%
	 &  & Torsion pairs and 3-fold flops \hfill 2025                                       \\
	 &  & \emph{Preprint.}
	\href{https://arxiv.org/abs/2502.05146}{arXiv:2502.05146}
	\nextItem%
	 &  & Kleinian orbifolds, cohomological Hall algebras, and Yangians
	\hfill 2025                                                                            \\
	 &  & (Joint with F. Sala and O. Schiffmann) \emph{In preparation.}
	\nextSection%
	\multirow{2}{0.8in}{\raggedleft\arraybackslash Selected talks (invited)}%
	 &  & Algebraic geometry seminar, University of Cambridge, \emph{Cambridge.}
	\hfill Nov 2025\nextItem%
	 &  & Mathematics--String theory seminar, Kavli IPMU, \emph{Tokyo.}
	\hfill Apr 2025\nextItem%
	 &  & Tokyo--Nagoya algebra seminar, University of Tokyo, \emph{Tokyo.}
	\hfill Apr 2025\nextItem%
	 &  & Algebraic geometry seminar, Tokyo Metropolitan University, \emph{Tokyo.}
	\hfill Apr 2025\nextItem%
	 &  & Algebraic geometry seminar, University of Liverpool, \emph{Liverpool.}
	\hfill Mar 2025\nextItem%
	 &  & Artin groups meet triangulated categories, MFO, \emph{Oberwolfach.}
	\hfill Jan 2024\nextItem%
	(contributed)%
	 &  & Simple-mindedness, silting, and stability, \emph{Ambleside.}
	\hfill Jul 2024\nextSection%
	\multirow{2}{0.8in}{\raggedleft\arraybackslash Teaching \& outreach}%
	 &  & \textbf{Tutor and Demonstrator}, University of Glasgow \hfill
	2022--25                                                                               \\[0.25em]
	 &  & \begin{minipage}[c]{4.3in}
		      Ran problem sessions for fourth year (\emph{Differential geometry}),
		      third year (\emph{Metric and topological spaces}), and second year
		      (\emph{Mechanics, Multivariable calculus, Mathematical methods and
			      modelling, Linear algebra, Graph theory, Discrete mathematics})
		      undergraduate mathematics courses.
	      \end{minipage}              \\\\[-0.6em]
	 &  & \textbf{Tutor}, \href{https://www.agq-cdt.org/count-me-in/}{Count me
	in}, University of Edinburgh \hfill 2024                                               \\[0.25em]
	 &  & \begin{minipage}[c]{4.3in}
		      Co-supervised (with Prof.\ Dhruv Ranganathan) two undergraduates
		      through a six week research project on \emph{Computing Euler
			      characteristics of moduli spaces of line arrangements}.
	      \end{minipage}                  \\\\[-0.6em]
	 &  & \textbf{Tutor}, Sutton Trust Summer School, Cambridge \hfill
	2019, 2021                                                                             \\[0.25em]
	 &  & \begin{minipage}[c]{4.3in}
		      Ran problem sessions, organised workshops, and conducted mock interviews
		      for university applicants from underrepresented groups.
	      \end{minipage}          \\\\[-0.4em]
	Organisation
	%	 &  & Algebra, Geometry, and Quantum fields (AGQ) student conference.\hfill 2025\nextItem
	 &  & Glasgow--Edinburgh Algebra Research Seminar (GEARS).\hfill 2025\nextItem%
	 &  & Glasgow Algebra Pre-Seminar (GAPS).\hfill 2023, 2024\nextSection%
	Other roles
	 &  & \textbf{President}, The Archimedeans (Cambridge University
	Mathematics Society). \hfill 2020, 2021\nextItem%
	 &  & \textbf{Social programme coordinator}, International Mathematics
	Olympiad. \hfill 2020, 2021
\end{longtable}
\end{document}
